### 2021-04-09 input/proposal.tex
wip

To identify and solve the issue with dynamic consistent partitioning
where protocols enable processes to \texttt{Add} and \texttt{Del} at
any time, we need to further constrain the delivery order at each
process.

@@

@@

\begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
  Eventual consistent partitioning in presence of dynamic sources
  requires
  \begin{inparaenum}[(i)]
  \item eventual purging of stale notifications, and
  \item eventual delivery of bests partitions.
  \end{inparaenum}
\end{corollary}

>>>>

One could solve this issue by always propagating the $\delta$ messages
corresponding to the $\alpha$ messages it propagated before. In
Figure~\ref{fig:problem}, it means that as soon as Process~$b$
forwards $\alpha_a^2$, it assumes that its neighbors Process~$c$ and
Process~$d$ may need the notification of removal $\delta_a$ if it
exists. However, such solution also implies that processes generate
traffic not only related to their current partition, but also related
to partitions they belong to in the past. Instead, we propose to use
the delivery order at each process to detect possible inconsistencies
and solve them. Together, processes eventually remove all stale
control information (transiting messages and local states) of the
system leaving room for propagation of messages about up-to-date
partitions.

%% To identify and solve the issue with dynamic consistent partitioning
%% where protocols enable processes to \texttt{Add} and \texttt{Del} at
%% any time, we need to further constrain the delivery order at each
%% process.

@@

\begin{corollary}[\label{theo:dcp}Dynamic consistent partitioning]
  Consistent partitioning where each process can \texttt{Add} and
  \texttt{Del} its partition at any time requires 
  \begin{inparaenum}[(i)]
  \item eventual purging of stale notifications, and
  \item eventual delivery of bests partitions.
  \end{inparaenum}
\end{corollary}

@@
